Ice sheet mass flows

### 2025-08-21 sankey.tex
Properly handle frontal advance and retreat
Make frontal advance optional in Sankey diagrams

First, unify advance and retreat

If advance > retreat,
  subtract retreat from advance, and set retreat to 0
If advance < retreat
  subtract advance from retreat and set advance to 0

Then, put it in terms of calving, or calving and frontal melt

AQ: Add retreat and subtract advance from calving

GL: Add (retreat - advance)/2 to calving and again frontal melt.

    \sankeyset{
      %% comment for gray outline
      %% draw/.style={
      %%   draw=white,
      %%   line width=0pt,line cap=round,line join=round,
      %% },
      %% comment for gray outline
      draw/.style={
        draw=black,
        line width=0.1mm,line cap=round,line join=round,
      },
      start style=arrow,end style=arrow,
      %% fill/.style={fill=yellow!10,line width=0pt,draw=yellow!10},
      ratio=1mm/60,
      minimum radius=0mm,
      water/.style={fill/.style={draw=water,line width=0pt,fill=water,},},
      ice/.style={fill/.style={draw=ice,line width=0pt,fill=ice,},},
      air/.style={fill/.style={draw=air,line width=0pt,fill=air,},},
      black/.style={fill/.style={draw=black,line width=0pt,fill=black,},},
      red/.style={fill/.style={fill=none, top color=red, bottom color=red},},
      ice-to-water/.style={fill/.style={fill=none, left color=ice, right color=water},},
      ice-to-air/.style={fill/.style={fill=none, left color=ice, right color=air},},
      ice-to-black/.style={fill/.style={fill=none, left color=ice, right color=black},},
      ice-to-air-vert/.style={fill/.style={fill=none, top color=ice, bottom color=air},},
      ice-to-water-vert/.style={fill/.style={fill=none, bottom color=ice, top color=water},},
      water-to-air-vert/.style={fill/.style={fill=none, right color=water, left color=air},},
      water-to-air/.style={fill/.style={fill=none, left color=water, right color=air},},
      air-to-ice/.style={fill/.style={fill=none, left color=air, right color=ice},},
      red-to-ice/.style={fill/.style={fill=none, left color=red, right color=ice},},
      water-to-ice/.style={fill/.style={fill=none, left color=water, right color=ice},},
      black-to-ice/.style={fill/.style={fill=none, bottom color=ice, top color=black},},
      in-black/.style={draw/.style={draw=gray,thick=3},},
      out-red/.style={draw/.style={draw=red,thick=3},},
      out-blue/.style={draw/.style={draw=water,thick=3},},
      debug label/.style={
        overlay,
        draw,
        font=\tiny,
        text=debug color,text opacity=1,
        inner sep=.1em,
        fill=white,fill opacity=0.5,
        rounded corners=.1em,
        node contents={\name: \qty},
        %node contents={\qty},
        %% node contents={\name},
      },
    }

@@

      \sankeynode{name=FRONTRETa, quantity=\qq{FRONTRET},
        at={[yshift=-\yoff]SHELFMELT.right}}
      \sankeynode{name=CALVa, quantity=\qq{CALV},
        at={[yshift=\yoff,xshift=0mm]SHELFMELTa.left}, anchor=right}
      \sankeynode{name=FRONTRETa, quantity=\qq{FRONTRET},
        at={[yshift=-\yoff]SHELFMELTa.right}, anchor=left}
    }

@@

    %% \sankeynode{name=FRONTRETa, quantity=\qq{FRONTRET}, at={[yshift=-\yoff]SHELFMELTa.right}}
    \sankeyoutin[out-blue]{FRONTRET}{FRONTRETa};

    \sankeynode{name=GZa, quantity=\qq{GZ}, at={[yshift=-\yoff]FRONTRETa.right}, anchor=left}

@@

    \sankeyoutin[ice-to-water]{GZ}{GZa}; \sankeyadvance[water]{GZa}{10mm};
    \sankeyend[water]{GZa}; \labelright{GZa}{vGZRET}
    \sankeyadvance[out-blue]{FRONTRETa}{10mm}; 
    \sankeyend[out-blue]{FRONTRETa}; \labelright{FRONTRETa}{vFRONTRET}

>>>>

    \sankeyset{
      %% comment for gray outline
      %% draw/.style={
      %%   draw=white,
      %%   line width=0pt,line cap=round,line join=round,
      %% },
      %% comment for gray outline
      draw/.style={
        draw=black,
        line width=0.1mm,line cap=round,line join=round,
      },
      start style=arrow,end style=arrow,
      %% fill/.style={fill=yellow!10,line width=0pt,draw=yellow!10},
      ratio=1mm/40,
      minimum radius=0mm,
      water/.style={fill/.style={draw=water,line width=0pt,fill=water,},},
      ice/.style={fill/.style={draw=ice,line width=0pt,fill=ice,},},
      air/.style={fill/.style={draw=air,line width=0pt,fill=air,},},
      black/.style={fill/.style={draw=black,line width=0pt,fill=black,},},
      red/.style={fill/.style={fill=none, top color=red, bottom color=red},},
      ice-to-water/.style={fill/.style={fill=none, left color=ice, right color=water},},
      ice-to-air/.style={fill/.style={fill=none, left color=ice, right color=air},},
      ice-to-black/.style={fill/.style={fill=none, left color=ice, right color=black},},
      ice-to-air-vert/.style={fill/.style={fill=none, top color=ice, bottom color=air},},
      ice-to-water-vert/.style={fill/.style={fill=none, bottom color=ice, top color=water},},
      water-to-air-vert/.style={fill/.style={fill=none, right color=water, left color=air},},
      water-to-air/.style={fill/.style={fill=none, left color=water, right color=air},},
      air-to-ice/.style={fill/.style={fill=none, left color=air, right color=ice},},
      red-to-ice/.style={fill/.style={fill=none, left color=red, right color=ice},},
      water-to-ice/.style={fill/.style={fill=none, left color=water, right color=ice},},
      black-to-ice/.style={fill/.style={fill=none, bottom color=ice, top color=black},},
      in-black/.style={draw/.style={draw=gray,thick=3},},
      out-red/.style={draw/.style={draw=red,thick=3},},
      out-blue/.style={draw/.style={draw=water,thick=3},},
      debug label/.style={
        overlay,
        draw,
        font=\tiny,
        text=debug color,text opacity=1,
        inner sep=.1em,
        fill=white,fill opacity=0.5,
        rounded corners=.1em,
        node contents={\name: \qty},
        %node contents={\qty},
        %% node contents={\name},
      },
    }

@@

      \ifnum \numexpr\Q{vFRONTRET} > 0
        \sankeynode{name=FRONTRETa, quantity=\qq{FRONTRET},
          at={[yshift=-\yoff]SHELFMELT.right}}
        \sankeynode{name=FRONTRETa, quantity=\qq{FRONTRET},
          at={[yshift=-\yoff]SHELFMELTa.right}, anchor=left}
      \fi
      \sankeynode{name=CALVa, quantity=\qq{CALV},
        at={[yshift=\yoff,xshift=0mm]SHELFMELTa.left}, anchor=right}
    }

@@

    %% \sankeynode{name=FRONTRETa, quantity=\qq{FRONTRET}, at={[yshift=-\yoff]SHELFMELTa.right}}
    \ifthenelse{\Q{vFRONTRET} > 0} {
      \sankeyoutin[out-blue]{FRONTRET}{FRONTRETa};
      \sankeynode{name=GZa, quantity=\qq{GZ}, at={[yshift=-\yoff]FRONTRETa.right}, anchor=left}
      \sankeyadvance[out-blue]{FRONTRETa}{10mm}; 
      \sankeyend[out-blue]{FRONTRETa}; \labelright{FRONTRETa}{vFRONTRET}
    } {
      \sankeynode{name=GZa, quantity=\qq{GZ}, at={[xshift=-10mm,yshift=-\yoff]SHELFMELTa.right}, anchor=left}
    }

@@

    \sankeyoutin[ice-to-water]{GZ}{GZa}; \sankeyadvance[water]{GZa}{10mm};
    \sankeyend[water]{GZa}; \labelright{GZa}{vGZRET}
